TBA

### 2020-10-06 spectral radius of matrix new method/slides/corre_mis1019.tex
full essay slide 1006 present

\documentclass[12pt]{article}
%\usetheme{Warsaw}
\usepackage{times}  % fonts are up to you
\usepackage{amssymb, amsmath, mathrsfs,amsthm}
\usepackage{multicol}
\usepackage{bm}
\usepackage{ulem}

\usepackage{fontspec}
\usepackage{xeCJK}
%\setCJKmainfont{微軟正黑體}
\setCJKmainfont{simsun.ttf}
\setCJKsansfont{simhei.ttf}
\setCJKmonofont{simfang.ttf}
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt

% THEOREMS ---------------------------------------------------------------
\theoremstyle{plain}
% block中的字會變成數學體, 斜體字
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{pf}[thm]{Proof}

@@

\newtheorem{algo}[thm]{Algorithm}

\title{TBA}
\author{Ke-Han Chen\\} % 作者
%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
\date{October 18th, 2018}
\date{\today} % 日期

\maketitle
\begin{abstract}
    This is my abstract.
\end{abstract}

\section{Preliminaries}

\begin{defn}
Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
\end{defn}
\begin{defn}
    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$. 
\end{defn}
    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix. 
    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$. 
\end{defn}

\thm
        If $C$ is nonnegative square matrix, then the following holds. \\
        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.

The following theorem is from [].

\begin{thm}
 Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]    $PCQ\leq PC'Q$;
\item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
\item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
\item[(iv)] $v^TPQu>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
    Moreover, $\lambda=\lambda'$ 
if and only if
    \begin{equation*}
        \label{e3}
(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
\end{equation*}
\end{thm}

\begin{pf}
            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
        \begin{equation}
            \label{e1}
            PCQu\leq PC'Qu=\lambda'PQu.
        \end{equation}
        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
        \begin{equation}
            \label{e2}
            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
        \end{equation}
        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.

        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.  Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
            $\lambda=\lambda'$ by (\ref{e2}). \qed

 \end{pf}

 Throughout fix $k\in [n-1]$. Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the  position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & 1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix}.$$
\begin{defn}\label{v_rooted}
 ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}
If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

\section{Our first result}

\begin{thm} \label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[-|n)\leq C'[-|n)$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
\item[(b)]
$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
\end{enumerate} \qed
\end{thm}

{\bf $k$-rooted matrix}

\begin{defn}[(k,n)-sum]
For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
\end{defn}

\begin{defn}[k-rooted matrix]\label{m_rooted}
A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
\end{defn}

\begin{thm}
Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
    \begin{enumerate}
        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
        \item[(ii)]$C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$ as an eigenvalue. $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
    \end{enumerate}

\begin{pf}
\subsection{}
(i) is immediate from Definition~\ref{m_rooted} and the observation that 
$$Q^{-1}=I-E_{kn}=\begin{pmatrix}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & -1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix},$$
and $Q^{-1}C'Q$ is 
$$\begin{pmatrix}
c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
\vdots \\
c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
\vdots              & \vdots & \ddots              & \vdots & \vdots \\
c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
\end{pmatrix}.
$$

\subsection{(ii)}

By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted. 
Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have 
$C'Qu=\rho(C')Qu$.

\subsection{(iii)}

Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.

\end{pf}
\end{thm}

@@

\section{Conclusion}

\begin{thm}
Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
such that $c'_{ij}\geq c_{ij}$, and then choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and 
let $c'_{in}:=r'_i-c'_{ik}$ with $r'_k \geq r'_n$. Whereas $c'_{kk}\geq c'_{nk}$ is not necessary. Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$. 
\end{thm}

{\bf Proof}

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by \ref{l_diag}, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$. So C'+d*I and C+d*I meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed

{Example}
For the following $4\times 4$ matrix
$$C=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 1\\
1 & 1 & 1 & 0
\end{pmatrix},$$
we choose
$$C'=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 1 &  0\\
1 & 1 & 0 & 1\\
1 & 1 & 1 & 0
\end{pmatrix}.$$
Then
$\rho(C)\leq \rho(C')$ by previous theorem.

{\bf Counterexample}
For the following two $4\times 4$ matrices
$$C=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 0
\end{pmatrix},\quad C'=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 1 &  0\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 0
\end{pmatrix},$$ 
we have $CQ\leq C'Q$, but 
$\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.

>>>>

\documentclass[]{beamer}
%\usetheme{Warsaw}
\usepackage{times}  % fonts are up to you
\usepackage{amssymb, amsmath, mathrsfs}
\usepackage{multicol}
\usepackage{bm}
\usepackage{ulem}

\usepackage{fontspec}
\usepackage{xeCJK}
\setCJKmainfont{微軟正黑體}
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt

% THEOREMS ---------------------------------------------------------------
\theoremstyle{plain}
% block中的字會變成數學體, 斜體字
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{remark}[thm]{Remark}

@@

\newtheorem{algo}[thm]{Algorithm}
%--------------------------------------------------------------------------
\setbeamertemplate{footline}[page number]{}
% 加頁碼, 到資料夾裡可以改得更徹底
\setbeamertemplate{navigation symbols}
% 加這行會把outline顯示在最上層

\usepackage{comment}

\title[]{TBA}
\author[]{Ke-Han Chen} % 作者
\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
\date{October 6th, 2020}
%\date{\today} % 日期

\begin{frame}
    \maketitle
\end{frame}

\begin{frame}
    \frametitle{Preliminaries}
    Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers respectively.

    \begin{defn}
        Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
        Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
    \end{defn}

    \begin{defn}

    When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
    $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
    where $|\lambda|$ is the magnitude of complex number $\lambda.$
    \end{defn}
\end{frame}

\begin{frame}
    \frametitle{Preliminaries}

    We are interested in spectral radius of the following matrix associated with a simple graph.

    \begin{defn} Given an undirected graph
    G, the$\textit{ adjacency matrix}$ of G is the square matrix $A = (a_{ij})$ indexed by vertices of G,
    and
    \[a_{ij} =\begin{cases}
    1, \text{if $i$ is adjacent to $j$}, \\
    0, \text{otherwise.}
    \end{cases}
    \]

    \end{defn}

    \begin{defn}
    Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral radius of the adjacency matrix of G.
    \end{defn}

\end{frame}

\begin{frame}
    \frametitle{Preliminaries}
    We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
    \begin{defn}
        For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column indices of 
        $C$ respectively,  We use $C[\alpha|\beta]$ to denote the submatrix of $C$ with size
         $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
    \end{defn}

\end{frame}

\begin{frame}
    \frametitle{ Preliminaries}

%The following theorem is from [].\cite{content}

    \begin{thm}
        Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
        Assume that
        \begin{enumerate}
            \item[(i)]    $PCQ\leq PC'Q$;
            \item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
            \item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
            such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
            \item[(iv)] $v^TPQu>0.$
            \end{enumerate}
            Then $\lambda\leq \lambda'$.
                Moreover, $\lambda=\lambda'$ 
            if and only if
                \begin{equation*}
                    \label{e3}
            (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
        \end{equation*}
    \end{thm}
\end{frame}

\begin{frame}
    \frametitle{ Proof}
            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
        \begin{equation}
            \label{e1}
            PCQu\leq PC'Qu=\lambda'PQu.
        \end{equation}
        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
        \begin{equation}
            \label{e2}
            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
        \end{equation}
        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
\end{frame}

\begin{frame}
    \frametitle{ Proof (Continue)}
        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.  Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$ 
         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
            $\lambda=\lambda'$ by (\ref{e2}).
\end{frame}

\begin{frame}
    \frametitle{ Our Method}

 Throughout fix $k\in [n-1]$. Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the  position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & 1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix}.$$

\end{frame}

\begin{frame}
    \frametitle{ $k$-rooted vector}

\begin{defn}
 A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}{vector rooted lemma}
If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

\end{frame}

\begin{frame}
    \frametitle{ Our first result}

\begin{thm} \label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
\item[(b)]
$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
\end{enumerate} \qed
\end{thm}
\end{frame}

\begin{frame}{}

    \begin{proof}
        The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1})  $.%!!!!!!!! 
        The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. 
        Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and 
        Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv) 
        of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  
        Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover $\lambda = \lambda'$ 
        if and only if (\ref{pre0}) holds, and this is equivalent to conditions (a),(b),(c) of this theorem. 
        \end{proof}

\end{frame}

\begin{frame}
    {\bf $k$-rooted matrix}
    \begin{defn}[(k,n)-sum]
        For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
    \end{defn}

    \begin{defn}[k-rooted matrix]\label{m_rooted}
        A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
    \end{defn}
\end{frame}

\begin{frame}

    \begin{thm} \label{lma_m_rooted}
        Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
            \begin{enumerate}
                \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
                \item[(ii)]Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
                \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
            \end{enumerate}
        \end{thm}

\end{frame}

\begin{frame}
    \frametitle{Remark}

    $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
    1 &  & & &  & 0 \\
    & 1 &  &      &  &  \\
    &  & \ddots & &  & -1 \\
    &  &        & &  &  \\
    &  & & & 1 &  \\
    0 &  & & &  & 1 \\
    \end{pmatrix}.$$

    The matrix $Q^{-1}C'Q$ is
    $$\begin{pmatrix}
    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
    \vdots \\
    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.
    $$
\end{frame}

\begin{frame}{Remark}

	\begin{proof}
        (i) is immediate from Definition~\ref{m_rooted} and the observation that   
        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
        1 &  & & &  & 0 \\
         & 1 &  &      &  &  \\
         &  & \ddots & &  & -1 \\
         &  &        & &  &  \\
          &  & & & 1 &  \\
        0 &  & & &  & 1 \\
        \end{pmatrix},$$
    \end{proof}

\end{frame}

\begin{frame}
    \begin{proof}
        and $Q^{-1}C'Q$ is
        $$\begin{pmatrix}
        c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
        \vdots \\
        c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
        c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
        \vdots              & \vdots & \ddots              & \vdots & \vdots \\
        c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
        \end{pmatrix}.$$
    \end{proof}
\end{frame}

\begin{frame}
    \begin{proof}{Continue}
        (ii)
            By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.  
            Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
            $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
            $C'Qu=\rho(C')Qu$.

        (iii)
        Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.

    \end{proof}
\end{frame}

\begin{frame}

@@

\end{frame}

\begin{frame}

\begin{thm}
    Let $C$ be an $n\times n$ nonnegative Tmatrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
    such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
    $r'_k \geq r'_n$. Moreover choose $c'_{in}:=r'_i-c'_{ik}$. Then $\rho(C)\leq \rho(C')$, when $C'=(c'_{ij})$.
\end{thm}

\end{frame}

\begin{frame}
    \frametitle{ Proof}

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by *, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$. So C'+d*I and C+d*I meet the conditions of (\ref{l_diag}), and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed

\end{frame}

\begin{frame}
    \frametitle{ Example}
    For the following $4\times 4$ matrix
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$
    we choose
    $$C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix}.$$
    Then
    $\rho(C)\leq \rho(C')$ by previous theorem.
\end{frame}

\begin{frame}
    \frametitle{Counterexample}
    For the following two $4\times 4$ matrices
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 0\\
    1 & 1 & 1 & 0
    \end{pmatrix},\quad C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 0\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$ 
    we have $CQ\leq C'Q$, but 
    $\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
    This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$. 
\end{frame}
